Radial Velocity Upper Limits on Planets around GJ\,1151

### 2019-06-17 paper/ms.tex
tim's not on this one

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).

>>>>

High stellar UV flux and flaring are thought to pose serious problems for habitability of planets around M~dwarfs \citep{Shields16,2019AsBio..19...64T}, though this may be not sufficiently severe in comparison to the early Earth to prevent the emergence of life \citep{2019MNRAS.485.5598O}. The stellar wind potentially poses a more severe problem. Star-planet interactions analogous to the magnetic interaction of Jupiter and Io are theorized to occur when a planet lies within the Alfv\'{e}n surface of their host star, where the planet is magnetically connected to its star and their magnetospheres are not separated by shocks. This is thought to be the case for Proxima~Centauri~b \citep{2016ApJ...833L...4G} and the inner TRAPPIST-1 planets \citep{2017ApJ...843L..33G}. With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres, but observational signatures of this have not so far been detected.

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization and low X-ray luminosity consistent with a possible star-planet magnetic interaction.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
